Manuscript plots

### 2023-11-15 manuscript_modelling_and_plots.Rmd
NASA TLX Scores per participant

```{r}
# Setting digits to 15 mins that fixation duration s are not rounded to annoying precise. 
options(digits = 15)
example.fixation <- fread(file = here::here("gaze_entropy_heterogenous/data/example.fixation.csv"))
```

@@

```{r}
# select demographic data such as age, annual miles driven, years with license
participant.info <- read.csv(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Data/participant_info.csv")) %>%
  dplyr::select(1:4, 7) %>%
  dplyr::rename("age" = "ï..Age", "ppid" = "Participant.ID")

@@

```{r}
nasa.tlx.mental <- fread(file = here::here("ITS/Work package 6.5 (HiDrive)/TME study/Data/NASA_TLX_scores.csv")) %>%
  dplyr::mutate(n_back = case_when(task == "N-back" ~ TRUE,
                                   task == "No N-back" ~ FALSE)) %>%
  dplyr::filter(sub_scale == "mental_demand") %>%
  dplyr::mutate(ppid = participant)
```

@@

```{r}
# maximum pitch and yaw coordinates
maxY = max(fixations$pitch)
maxX = max(fixations$yaw)

# minimum pitch and yaw coordinates
minY = min(fixations$pitch)
minX = min(fixations$yaw)

# example trial - this can be any trial
example <- fixations %>%
  dplyr::filter(trialid == "9_FALSE_6_3")

# creating state spaces - cuts the x and y coordinates into 3 degree chunks 
example <- example %>%
  dplyr::mutate(x_range = cut(yaw, seq(minX, maxX, by = 3), right = FALSE)) %>%
  dplyr::mutate(y_range = cut(pitch, seq(minX, maxY, by = 3), right = FALSE))

# state space coordinates
state_space_coordinates <- example %>%
  dplyr::group_by(x_range, y_range) %>%
  dplyr::summarise(count = n()) %>%
  dplyr::ungroup()  %>%
  tidyr::complete(x_range, y_range) %>%
  dplyr::mutate(state_space = row_number()) %>%
  dplyr::mutate(x_range_2 = x_range, y_range_2 = y_range) %>%
  tidyr::separate_wider_delim(x_range, ",", names = c("x_lower", "x_upper")) %>%
  tidyr::separate_wider_delim(y_range, ",", names = c("y_lower", "y_upper")) %>%
  dplyr::mutate(x_lower = str_replace_all(x_lower, "\\[|\\]", ""), x_upper = str_replace_all(x_upper, "\\(|\\)", "")) %>%
  dplyr::mutate(y_lower = str_replace_all(y_lower, "\\[|\\]", ""), y_upper = str_replace_all(y_upper, "\\(|\\)", "")) %>%
  dplyr::mutate(x_lower = as.numeric(x_lower), x_upper = as.numeric(x_upper), y_lower = as.numeric(x_lower), y_upper = as.numeric(x_upper))

# plot the state space grids alongside the fixation coordinates 
fixation_state_space <- ggplot() +
  geom_vline(state_space_coordinates, mapping = aes(xintercept = x_upper), col = "grey") +
  geom_hline(state_space_coordinates, mapping = aes(yintercept = y_upper), col = "grey") +
  geom_vline(state_space_coordinates, mapping = aes(xintercept = x_lower), col = "grey") +
  geom_hline(state_space_coordinates, mapping = aes(yintercept = y_lower), col = "grey") +
  geom_point(example, mapping = aes(yaw, pitch, col = fixation_number), size = .6) +
  scale_colour_continuous(name = "Fixation number", type = "viridis", breaks = c(25, 75, 125)) +
  ylab("Pitch (°)") +
  xlab("Yaw (°)") +
  ylim(-20, 10) +
  xlim(-40, 50) +
  theme_plot +
  theme(legend.position = "bottom", legend.key.width = unit(1, 'cm'), legend.key.height = unit(.3, 'cm'))

# data saving   
ggsave(here::here("ITS/Work package 6.5 (HiDrive)/TME study/Analysis/Plots/manuscript plots/fixation_state_space .tiff"), plot = fixation_state_space , width = 12, height = 8, units = 'cm', dpi = 600, type = 'cairo')
```

>>>>

```{r}
# Setting digits to 15 mins that fixation duration s are not rounded to annoying precise values. 
options(digits = 15)
example.fixation <- fread(file = here::here("gaze_entropy_heterogenous/data/example.fixation.csv"))
```

@@

```{r}
# select demographic data such as age, annual miles driven, years with license
participant.info <- read.csv(here::here("gaze_entropy_heterogenous/data/participant_info.csv")) %>%
  dplyr::select(1:5) %>%
  dplyr::rename("age" = "ï..Age", "ppid" = "Participant.ID")

@@

```{r}
nasa.tlx.mental <- fread(file = here::here("gaze_entropy_heterogenous/data/NASA_TLX_scores.csv")) %>%
  dplyr::mutate(n_back = case_when(task == "N-back" ~ TRUE,
                                   task == "No N-back" ~ FALSE)) %>%
  dplyr::filter(sub_scale == "mental_demand") %>%
  dplyr::mutate(ppid = participant)
```

@@

```{r}
# maximum pitch and yaw coordinates
maxY = max(example.fixation$pitch)
maxX = max(example.fixation$yaw)

# minimum pitch and yaw coordinates
minY = min(example.fixation$pitch)
minX = min(example.fixation$yaw)

# creating state spaces - cuts the x and y coordinates into 3 degree chunks 
example.fixation <- example.fixation %>%
  dplyr::mutate(x_range = cut(yaw, seq(minX, maxX, by = 3), right = FALSE)) %>%
  dplyr::mutate(y_range = cut(pitch, seq(minX, maxY, by = 3), right = FALSE))

# state space coordinates
state_space_coordinates <- example.fixation %>%
  dplyr::group_by(x_range, y_range) %>%
  dplyr::summarise(count = n()) %>%
  dplyr::ungroup()  %>%
  tidyr::complete(x_range, y_range) %>%
  dplyr::mutate(state_space = row_number()) %>%
  dplyr::mutate(x_range_2 = x_range, y_range_2 = y_range) %>%
  tidyr::separate_wider_delim(x_range, ",", names = c("x_lower", "x_upper")) %>%
  tidyr::separate_wider_delim(y_range, ",", names = c("y_lower", "y_upper")) %>%
  dplyr::mutate(x_lower = str_replace_all(x_lower, "\\[|\\]", ""), x_upper = str_replace_all(x_upper, "\\(|\\)", "")) %>%
  dplyr::mutate(y_lower = str_replace_all(y_lower, "\\[|\\]", ""), y_upper = str_replace_all(y_upper, "\\(|\\)", "")) %>%
  dplyr::mutate(x_lower = as.numeric(x_lower), x_upper = as.numeric(x_upper), y_lower = as.numeric(x_lower), y_upper = as.numeric(x_upper))

# plot the state space grids alongside the fixation coordinates 
fixation_state_space <- ggplot() +
  geom_vline(state_space_coordinates, mapping = aes(xintercept = x_upper), col = "grey") +
  geom_hline(state_space_coordinates, mapping = aes(yintercept = y_upper), col = "grey") +
  geom_vline(state_space_coordinates, mapping = aes(xintercept = x_lower), col = "grey") +
  geom_hline(state_space_coordinates, mapping = aes(yintercept = y_lower), col = "grey") +
  geom_point(example.fixation, mapping = aes(yaw, pitch, col = fixation_number), size = .6) +
  scale_colour_continuous(name = "Fixation number", type = "viridis", breaks = c(25, 75, 125)) +
  ylab("Pitch (°)") +
  xlab("Yaw (°)") +
  ylim(-20, 10) +
  xlim(-40, 40) +
  theme_plot +
  theme(legend.position = "bottom", legend.key.width = unit(1, 'cm'), legend.key.height = unit(.3, 'cm'))

# data saving   
ggsave(here::here("gaze_entropy_heterogenous/plots/Fig4.tiff"), plot = fixation_state_space , width = 12, height = 8, units = 'cm', dpi = 300, type = 'cairo')
```
